---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# polymiss

<!-- badges: start -->
<!-- badges: end -->

The polymiss package provides a vector class, `polymiss`, that allows for representing different types of missing values.

## Installation

You can install from GitHub:

``` r
devtools::install_github("ngriffiths21/polymiss")
```

## Example

Regular `double()` vectors can be wrapped in a `polymiss()` in order to create more useful missing values.

Currently missing value types are represented as integers:

| `miss` | Value        | Explanation                              |
| ----   | ----         | ---                                      |
| 1L     | Non-missing  | Known value                              |
| 2L     | Unknown      | Missing, but a "true" value should exist |
| NA     | Non-existent | Missing, and no "true" value is possible |

To create a `polymiss()` vector:

```{r}
library(polymiss)
p1 <- polymiss(c(7, NA, NA), miss = c(1L, 2L, NA))
p1
```

To discard `<NONE>`, use `reduce()`:

```{r}
sum(p1)

p1[-2]
reduce(p1[-2], `+`)
```

## License

[MIT](https://choosealicense.com/licenses/mit/)
